---
title: "Plots and models"
output: html_document
---

1. Load packages and data file
```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(exactRankTests)
library(lme4)
library(langcog)
library(brms)
library(wordcloud)
library(RColorBrewer)
library(patchwork)
library(ngram)

##library(psychometric)
##library(multilevel)
##library(nlme)

##library(Rmisc)
##library(lattice)
##library(plyr)

## library(devtools)
## devtools::install_github("langcog/langcog")

data <- read.csv2("data_file_stimulus.csv")
data
```


2. Plots
2.1. Plots (hol versus seq) seperate for object_str, object_se, feature_str, feature_se (with: rel, irrel, ne)
```{r cars}
plot_1 <- ggplot(data = data, aes(x = condition, col = object_str)) +
  labs (x = "condition", y = "object_str") +
  geom_bar() 

plot_2 <- ggplot(data = data, aes(x = condition, col = feature_str)) +
  labs (x = "condition", y = "feature_str") +
  geom_bar() 

plot_3 <- ggplot(data = data, aes(x = condition, col = object_se)) +
  labs (x = "condition", y = "object_se") +
  geom_bar() 

plot_4 <- ggplot(data = data, aes(x = condition, col = feature_se)) +
  labs (x = "condition", y = "feature_se") +
  geom_bar() 

plot_1
plot_2
plot_3
plot_4

```


2.2. Create binary dependent variables 
```{r pressure, echo=FALSE}

## dependent variable: code 'rel' = 1 and 'irr or ne' = 0 -> enables comparison with respect to relevant answers (relevant object/feature or not) 
data_rel_not <- data %>%
  separate(stimulus_nc, c("object", "predicate"), remove = F) %>%
  mutate(object_str = ifelse(object_str == "rel", "1", "0"),
         object_str = as.numeric(as.character(object_str)),
         feature_str = ifelse(feature_str == "rel", "1", "0"),
         feature_str = as.numeric(as.character(feature_str)),
         object_se = ifelse(object_se == "rel", "1", "0"),
         object_se = as.numeric(as.character(object_se)),
         feature_se = ifelse(feature_se == "rel", "1", "0"),
         feature_se = as.numeric(as.character(feature_se)))

## dependent variable: code 'rel + irrel' = 1 and 'ne' = 0 -> enables comparison with respect to existence of an answer (does an object/feature exist or not)
data_ex_ne <- data %>%
  separate(stimulus_nc, c("object", "predicate"), remove = F) %>%
  mutate(object_str = ifelse(object_str == "ne", "0", "1"),
         object_str = as.numeric(as.character(object_str)),
         feature_str = ifelse(feature_str == "ne", "0", "1"),
         feature_str = as.numeric(as.character(feature_str)),
         object_se = ifelse(object_se == "ne", "0", "1"),
         object_se = as.numeric(as.character(object_se)),
         feature_se = ifelse(feature_se == "ne", "0", "1"),
         feature_se = as.numeric(as.character(feature_se)))
``` 



2.3. Plots - comparing hol versus seq seperate for feature and objects
```{r}
## dependent variable: 'rel' = 1 or 'irr + ne' = 0 
plot1 <- data_rel_not%>%
  select(-X, - repetitions, -X.1)%>%
  gather(dimension, correct,-condition, -id, -stimulus_nc, -object, -predicate, -responses)

plot2 <- plot1%>%
  group_by(condition, dimension)%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = dimension, y = correct, col = condition), position = position_jitterdodge(jitter.width = .2, jitter.height = 0.05,dodge.width = 0.5), alpha = .3)+
  geom_pointrange(data = plot2,aes(x = dimension, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 0.6, pch = 5) +
  guides(alpha = F)+
  labs(x="Picture")+
  scale_y_continuous(name = "Relevance (Proportion correct)", limits = c(-0.05,1.05))+
  theme_few() + 
  scale_colour_solarized()


## dependent variable: 'rel + irrel' = 1 or 'ne' = 0
plot3 <- data_ex_ne%>%
  select(-X, - repetitions, -X.1)%>%
  gather(dimension, correct,-condition, -id, -stimulus_nc,-object, -predicate, -responses)

plot4 <- plot3%>%
  group_by(condition, dimension)%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot3, aes(x = dimension, y = correct, col = condition), position = position_jitterdodge(jitter.width = .2, jitter.height = 0.05,dodge.width = 0.5), alpha = .3)+
  geom_pointrange(data = plot4,aes(x = dimension, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 0.6, pch = 5) +
  guides(alpha = F)+
  labs(x="Picture")+
  scale_y_continuous(name = "Existence (Proportion correct)", limits = c(-0.05,1.05))+
  theme_few() + 
  scale_colour_solarized()
```


2.4. Plots - comparing hol versus seq seperate for each category (object: mov, num, size) and (feature: animal, object)
```{r}
### dependent variable: 'rel' = 1 or 'irr + ne' = 0

## object_str
plot1 <- data_rel_not%>%
  select(-X, - repetitions, -X.1)%>%
  gather(dimension, correct,-condition, -id, -stimulus_nc, -object, -predicate, -responses) %>%
  filter (dimension == "object_str")

plot2 <- plot1%>%
  group_by(condition, object)%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = object, y = correct, col = condition), position = position_jitterdodge(jitter.width = .2, jitter.height = 0.05,dodge.width = 0.5), alpha = .3)+
  geom_pointrange(data = plot2,aes(x = object, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 0.6, pch = 5) +
  guides(alpha = F)+
  labs(x="Object")+
  scale_y_continuous(name = "Relevance (Proportion correct)", limits = c(-0.05,1.05))+
  theme_few() + 
  scale_colour_solarized()

## feature_str
plot1 <- data_rel_not%>%
  select(-X, - repetitions, -X.1)%>%
  gather(dimension, correct,-condition, -id, -stimulus_nc, -object, -predicate, -responses) %>%
  filter (dimension == "feature_str")

plot2 <- plot1%>%
  group_by(condition, predicate)%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = predicate, y = correct, col = condition), position = position_jitterdodge(jitter.width = .2, jitter.height = 0.05,dodge.width = 0.5), alpha = .3)+
  geom_pointrange(data = plot2,aes(x = predicate, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 0.6, pch = 5) +
  guides(alpha = F)+
  labs(x="Feature")+
  scale_y_continuous(name = "Relevance (Proportion correct)", limits = c(-0.05,1.05))+
  theme_few() + 
  scale_colour_solarized()


### dependent variable: 'rel + irrel' = 1 or 'ne' = 0

## object_str
plot1 <- data_ex_ne%>%
  select(-X, - repetitions, -X.1)%>%
  gather(dimension, correct,-condition, -id, -stimulus_nc, -object, -predicate, -responses) %>%
  filter (dimension == "object_str")

plot2 <- plot1%>%
  group_by(condition, object)%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = object, y = correct, col = condition), position = position_jitterdodge(jitter.width = .2, jitter.height = 0.05,dodge.width = 0.5), alpha = .3)+
  geom_pointrange(data = plot2,aes(x = object, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 0.6, pch = 5) +
  guides(alpha = F)+
  labs(x="Object")+
  scale_y_continuous(name = "Existence (Proportion correct)", limits = c(-0.05,1.05))+
  theme_few() + 
  scale_colour_solarized()

## feature_str
plot1 <- data_ex_ne%>%
  select(-X, - repetitions, -X.1)%>%
  gather(dimension, correct,-condition, -id, -stimulus_nc, -object, -predicate, -responses) %>%
  filter (dimension == "feature_str")

plot2 <- plot1%>%
  group_by(condition, predicate)%>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = plot1, aes(x = predicate, y = correct, col = condition), position = position_jitterdodge(jitter.width = .2, jitter.height = 0.05,dodge.width = 0.5), alpha = .3)+
  geom_pointrange(data = plot2,aes(x = predicate, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 0.6, pch = 5) +
  guides(alpha = F)+
  labs(x="Feature")+
  scale_y_continuous(name = "Existence (Proportion correct)", limits = c(-0.05,1.05))+
  theme_few() + 
  scale_colour_solarized()

```



3. Calculate baysian models

3.1. Data files for models
```{r}
## Number of words per response
data_wordcount <- data %>%
  separate(stimulus_nc, c("object", "predicate"), remove = F) %>%
  mutate(responses = ifelse(responses == "", NA, as.character(responses)))%>%
  group_by(id, object, predicate, condition, responses)%>%
  mutate(words = wordcount(responses)) %>%
  ungroup() %>%
  mutate(property = ifelse(predicate == "jump" | predicate == "run", "movement",
                           ifelse(predicate == "big" | predicate == "small", "size","number")),
         class = ifelse(object == "ball" | object == "bike" | object == "comb" | object == "bike" | object == "fork" | object == "hammer", "object","animal"))


## Existence of object AND feature in respone
data_of_structure <- data %>%
  separate(stimulus_nc, c("object", "predicate"), remove = F) %>%
  mutate(object_str = ifelse(object_str == "ne", "0", "1"),
         object_str = as.numeric(as.character(object_str)),
         feature_str = ifelse(feature_str == "ne", "0", "1"),
         feature_str = as.numeric(as.character(feature_str)),
         obj_fea = ifelse(object_str == 1 & feature_str == 1, "1", "0"),
         property = ifelse(predicate == "jump" | predicate == "run", "movement",
                           ifelse(predicate == "big" | predicate == "small", "size","number")),
         class = ifelse(object == "ball" | object == "bike" | object == "comb" | object == "bike" | object == "fork" | object == "hammer", "object","animal"),
         obj_fea = as.numeric(as.character(obj_fea)))
  
## Feature in response is relevant
data_fea_content <- data %>%
  separate(stimulus_nc, c("object", "predicate"), remove = F) %>%
  mutate (feature_str = ifelse(feature_str == "rel", "1", "0"),
          feature_str = as.numeric(as.character(feature_str))) %>%
  mutate(property = ifelse(predicate == "jump" | predicate == "run", "movement",
                           ifelse(predicate == "big" | predicate == "small", "size","number")),
         class = ifelse(object == "ball" | object == "bike" | object == "comb" | object == "bike" | object == "fork" | object == "hammer", "object","animal"))

```




3.2. dependent variable 'length' (hier keine binäre Codierung)
```{r}
## https://www.rdocumentation.org/packages/brms/versions/2.12.0/topics/brmsfamily
## wsh skew_normal wegen schiefer Verteilung

# m1_l <- glmer(characters ~ condition + (condition * predicate | id) + (1 | stimulus_nc), family = binomial, data = data_length,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

## ? in Präregistirierung ( 1 | stimulus), letztes Mal besprochen (condition | stimulus)

m1_l <- brm(words ~ condition * property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_wordcount, family = skew_normal(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m1_l.rds")

m1_l <- readRDS("../saves/m1_l.rds")


# m2_l <- glmer(characters ~ condition + predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_length,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m2_l <- brm(words ~ condition + property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_wordcount, family = skew_normal(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m2_l.rds")

m2_l <- readRDS("../saves/m2_l.rds")


# m3_l <- glmer(characters ~ predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_length,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m3_l <- brm(words ~ property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_wordcount, family = skew_normal(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m3_l.rds")

m3_l <- readRDS("../saves/m3_l.rds")


# model comparison 
loo_compare(m1_l, m2_l, m3_l, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Predictors")%>%
  mutate(
    Predictors = recode(Predictors, 
                   m1_l = "condition * Condition", 
                   m2_l = "Age + Condition",
                   m3_l = "Age"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 2),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Predictors, WAIC, SE, weight)
```


3.2. DV 'Object-feature structure' (Done)
```{r}
# Bayesian model object-feature structure

## m1_of <- glmer(obj_fea ~ condition * predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_of_structure,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m1_of <- brm(obj_fea ~ condition * property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_of_structure, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m1_of.rds")

m1_of <- readRDS("../saves/m1_of.rds")
## saved

## m2_of <- glmer(obj_fea ~ condition + predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_of_structure,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m2_of <- brm(obj_fea ~ condition + property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_of_structure, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m2_of.rds")

m2_of <- readRDS("../saves/m2_of.rds")


# m3_of <- glmer(obj_fea ~ predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_of_structure,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m3_of <- brm(obj_fea ~ property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_of_structure, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m3_of.rds")

m3_of <- readRDS("../saves/m3_of.rds")

# model comparison 
loo_compare(m1_of, m2_of, m3_of, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Predictors")%>%
  mutate(
    Predictors = recode(Predictors, 
                   m1_of = "condition * Condition", 
                   m2_of = "Age + Condition",
                   m3_of = "Age"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 2),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Predictors, WAIC, SE, weight)

```


3.3. DV 'Feature content' (TO DO Baysian Models correct)
```{r}
# m1_fc <- glmer(feature_str ~ condition * predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_fea_content,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m1_fc <- brm(feature_str ~ condition * property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_fea_content, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m1_fc.rds")

m1_fc <- readRDS("../saves/m1_fc.rds")


# m2_fc <- glmer(feature_str ~ condition + predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_fea_content,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m2_fc <- brm(feature_str ~ condition + property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_fea_content, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m2_fc.rds")

m2_fc <- readRDS("../saves/m2_fc.rds")


# m3_fc <- glmer(feature_str ~ predicate + (condition * predicate | id) + (1 | data$stimulus_nc), family = binomial, data = data_fea_content,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

m3_fc <- brm(feature_str ~ property + (condition * property | id) + (condition | stimulus_nc),
                    data = data_fea_content, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  add_criterion("waic")%>%
  saveRDS(.,"../saves/m3_fc.rds")

m3_fc <- readRDS("../saves/m3_fc.rds")


# model comparison 
loo_compare(m1_fc, m2_fc, m3_fc, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Predictors")%>%
  mutate(
    Predictors = recode(Predictors, 
                   m1_fc = "condition * Condition", 
                   m2_fc = "Age + Condition",
                   m3_fc = "Age"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 2),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Predictors, WAIC, SE, weight)
```



4. Word Clouds
4.1. Create data file for word clouds
```{r}
data_file <- read.csv2("data_file.csv")%>%
  select(-X)

data_words <- read.csv2("Words_data_codiert.csv")%>%
  select(-X)

data_wordcloud <- data_file %>%
  left_join(data_words)
```


4.2. Wordclouds for objects (objects/animals) (sepearate for hol versus seq)
```{r}
# par(mfrow=c(2,2))

## object (hol vs seq)
object_hol <- data_wordcloud %>%
  filter(type == "object", class == "object", condition == "hol") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = object_hol$value, freq = object_hol$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

object_seq <- data_wordcloud %>%
  filter(type == "object", class == "object", condition == "seq") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = object_seq$value, freq = object_seq$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))


## animal (hol vs seq)
animal_hol <- data_wordcloud %>%
  filter(type == "object", class == "animal", condition == "hol") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = animal_hol$value, freq = animal_hol$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

animal_seq <- data_wordcloud %>%
  filter(type == "object", class == "animal", condition == "seq") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = animal_seq$value, freq = animal_seq$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```


4.3. wordclouds for features (movement/number/size) (sepearate for hol versus seq)
```{r}
## movement (hol vs seq)
movement_hol <- data_wordcloud %>%
  filter(type == "feature", property == "movement", condition == "hol") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = movement_hol$value, freq = movement_hol$freq, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

movement_seq <- data_wordcloud %>%
  filter(type == "feature", property == "movement", condition == "seq") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = movement_seq$value, freq = movement_seq$freq, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))


## number (hol vs seq)
number_hol <- data_wordcloud %>%
  filter(type == "feature", property == "number", condition == "hol") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = number_hol$value, freq = number_hol$freq, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

number_seq <- data_wordcloud %>%
  filter(type == "feature", property == "number", condition == "seq") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = number_seq$value, freq = number_seq$freq, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))


## size (hol vs seq)
size_hol <- data_wordcloud %>%
  filter(type == "feature", property == "size", condition == "hol") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = size_hol$value, freq = size_hol$freq, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

size_seq <- data_wordcloud %>%
  filter(type == "feature", property == "size", condition == "seq") %>%
  select(value, freq) %>%
  distinct()

wordcloud(words = size_seq$value, freq = size_seq$freq, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```







(5. t-test + ANOVA) 

two.sided t.test (rel versus not) 

```{r}
## feature_str
t.test(feature_str ~ condition,
       alternative = c("two.sided"), data_rel_not)

## object_str
t.test(object_str ~ condition,
       alternative = c("two.sided"), data_rel_not)
```

```{r}
library("ez")

data_fea_contentANOVA <- data_fea_content %>%
  mutate(as.factor(predicate),
         as.factor(object),
         as.factor(condition)) %>%
  mutate(feature_str = ifelse(object_str == "rel", "2", "1"),
         as.numeric(feature_str)) %>%
  mutate(as.numeric(id))


ezANOVA_fea_content <- ezANOVA(data_fea_contentANOVA, dv=(feature_str), wid =(id),
                                   within =(condition), detailed = T,
                                   type=3)

ezAnova_PercCor <- ezANOVA(data_longPercCor, dv=.(Percent_Correct), wid=.(VPCode), 
                           between=.(Gruppe), within=.(Similarity, TestLanguage2), detailed = T, type=3)

```


